Parallel multi-objective optimization using co-evolutionary islands with overlapping search space

### 2016-12-18 hpmoon-coor.tex
Wondering about coevolution
This goes to the correct #15 issue.

To solve this issue, some authors have proposed the usage of Master-Slave approaches. For example,  \citep{Durillo08masterslave} compared different master-slave approaches: synchronous generational, asynchronous generational and asynchronous steady-state, being the latter the most promising option. The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power.

The work by Deb et al. \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of the solutions was divided into the islands using a coordinate transformation. Their authors concluded that dividing the search space is a good idea, although achieve this is not trivial. Dividing the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separation in processors by objective \citep{Xiao03specialized}. Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.

Addressing high-dimensional problems with cooperative coevolution has also been studied in several works with approaches more similar to the one presented here.
The approach to focus on a portion of the chromosome, as in our overlapped method, was firstly used in the work by Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining super-linear performance
in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
master-slave method that splits the population into several processors. As in previous work, each node
runs a parallel MOEA that only affects some portion of 
the individuals and the master
process receives all the sub-populations to be combined every certain number of generations. Up to 8 processors
were used in the experimental setup, and several
combination alternatives were compared. The main difference of our work with respect to previous works is that our approach does not 
broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper we have
used up to 128 islands.

>>>>

To solve this issue, some authors have proposed using Master-Slave approaches. For example,  \citep{Durillo08masterslave} compared different master-slave approaches: synchronous generational, asynchronous generational and asynchronous steady-state, being the latter the most promising option. The method proposed by Hiroyasu \citep{Hiroyasu07discussion} generates offspring depending on the computational power.

%This is an improvement over the previous? What is the relationship?
The work by Deb et al. \citep{Deb03distributed} was one of the first approaches for distributed MOEAs (dMOEAs). In that work, the dominance of the solutions was divided into the islands using a coordinate transformation. Their authors concluded that dividing the search space is a good idea, although achieve this is not trivial. Dividing the search space has been explored by other researchers, for example, dividing the population in elite and search sub-populations \citep{Wang09parallel}, or separation in processors by objective \citep{Xiao03specialized}. Other authors, such as Martens \citep{Martens13asynchronous} use migration to accept individuals based on diversity, and migrating from not-crowded areas.

% Is this really cooperative coevolution? - JJ
Addressing high-dimensional problems with cooperative coevolution has
also been studied in several works with approaches closer to the one
presented here. The approach to focus on a portion of the chromosome,
as in our overlapped method, was firstly used in the work by
Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
super-linear performance 
in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
master-slave method that splits the population into several processors. As in previous work, each node
runs a parallel MOEA that only affects some portion of 
the individuals and the master
process receives all the sub-populations to be combined every certain number of generations. Up to 8 processors
were used in the experimental setup, and several
combination alternatives were compared. The main difference of our work with respect to previous works is that our approach does not 
broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper we have
used up to 128 islands.
